Extension of the approximate static condensation method for multi-material diffusion problems to 3D

### 2019-08-12 3d/asc3d.tex
Add constant concentration on multi-material faces example

@@

>>>>

\begin{figure}[H]
	\centering
	\begin{subfigure}{.33\linewidth}
		\centering
		\includegraphicsw[.9]{{skewed_exact_k.cropped}.png}
	\end{subfigure}%
	\begin{subfigure}{.33\linewidth}
		\centering
		\includegraphicsw[.9]{{skewed_k.cropped}.png}
	\end{subfigure}%
	\begin{subfigure}{.33\linewidth}
		\centering
		\includegraphicsw[.9]{{skewed_vor_k.cropped}.png}
	\end{subfigure}%
	\vskip .3cm
	\begin{subfigure}{.33\linewidth}
		\centering
		\includegraphicsw[.9]{{skewed_exact.cropped}.png}
	\end{subfigure}%
	\begin{subfigure}{.33\linewidth}
		\centering
		\includegraphicsw[.9]{{skewed.cropped}.png}
	\end{subfigure}%
	\begin{subfigure}{.33\linewidth}
		\centering
		\includegraphicsw[.9]{{skewed_vor.cropped}.png}
	\end{subfigure}%	
	\caption{Computed solutions $p_h$. Left: Multi-material faces lie only in $xy$-plane, $\|p - p_h\|_{\lTwoSpace} = 1.08\times 10^{-14}$. Middle and right: Slightly perturbed interface so we have that $p$ is not constant on all multi-material faces, $\|p - p_h\|_{\lTwoSpace} = 3.10\times 10^{-10}$ (Middle) and $\|p - p_h\|_{\lTwoSpace} = 3.17\times 10^{-3}$ (Right)}
	\label{fig:skewed}		
\end{figure}

@@

Pic: $p_h$ + fluxes and error for cyl
